Men and Women Both Prefer and Perceive Inaction as More Competent: An Analysis of Preference and Perceived Competence of Actions and Inaction Agents in Risky Decisions Resulting in Negative Outcomes by Gender

### 2024-02-16 outputs/paper/paper.qmd
paper update

---
title: "An Analysis of Preference and Percieved Competence of Actions and Inaction Agents in Risky Decisions Resulting in Negative Outcomes by Gender: Men and Women Both Prefer and Percieve Inaction as More Competent"
author: 
- Francesca Ye 
- Sky Suh 
- Hari Lee Robledo
date: "today"
date-format: long
abstract: "This report investigates differences between gender and perceptions of action versus inaction agents from research conducted by Adrien et al. that broadly examined the perceptions of decision-making approaches. Focusing on preference and perceived competence this report graphed the frequencies of responses by gender in addition to statistical significance analysis from Fillion et al.’s  “Evaluations of Actions and Inaction Decision-makers in Risky Decisions Resulting in Negative Outcomes” Study 2 data. This report found there are no significant differences in preference and perceived competence by gender as both slightly leaned towards inaction for both estimands. Considering the larger field of moral judgment, this report indicates that gender does not seem to be a  strong influence on decision-making approaches as previously thought."
thanks: "Code and data from this analysis are available at: https://github.com/hari-lr/Preference-and-Perception-of-Decision-Making"
toc: true
number-sections: true
bibliography: references.bib
format: pdf
---

>>>>

---
title: "Men and Women Both Prefer and Perceive Inaction as More Competent: An Analysis of Preference and Perceived Competence of Actions and Inaction Agents in Risky Decisions Resulting in Negative Outcomes by Gender" 
subtitle: "A Further Investigation of Study 2 Data from “Evaluations of Action and Inaction Decision-makers in Risky Decisions Resulting in Negative Outcomes: Inaction Agents Are Preferred to and Perceived as More Competent and Normative Than Action Agents” by Adrien et al."
author: 
- Francesca Ye 
- Sky Suh 
- Hari Lee Robledo
date: "today"
date-format: long
abstract: "This report investigates differences between gender and perceptions of action versus inaction agents from research conducted by Adrien et al. that broadly examined the perceptions of decision-making approaches. Focusing on preference and perceived competence this report graphed the frequencies of responses by gender in addition to statistical significance analysis from Fillion et al.’s  “Evaluations of Actions and Inaction Decision-makers in Risky Decisions Resulting in Negative Outcomes” Study 2 data. This report found there are no significant differences in preference and perceived competence by gender as both slightly leaned towards inaction for both estimands. Considering the larger field of moral judgment, this report indicates that gender does not seem to be a  strong influence on decision-making approaches as previously thought."
thanks: "Code and data from this analysis are available at: https://github.com/hari-lr/Preference-and-Perception-of-Decision-Making"
toc: true
number-sections: true
bibliography: references.bib
format: pdf
---
